Supplementary material for 'The complex network of trophic interactions in a subAntarctic Marine Protected Area

### 2023-02-04 MS_ToSubmit/SupMaterial.Rmd
Fix NA in Table S3

# Table 2. List of species
knitr::kable(spp_total %>% 
               mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon",
                                          TRUE ~ TopRole)) %>% 
               dplyr::select(TrophicSpecies, FunctionalGroup, TotalDegree, NumPrey, NumPred, Between, Close, TL, meanTrophicSimil, TopRole) %>% 
               arrange(., desc(TotalDegree)) %>% 
               mutate(across(where(is.numeric), round, 4)), 
             format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Degree","NumPrey","NumPred","Between","Close","TL","TS","TR"), align = "llcccccccc", caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem. Ordered by degree (total number of interactions). Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4.5)

>>>>

# Table 2. List of species
knitr::kable(spp_total %>% 
               mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon",
                                          TRUE ~ TopRole)) %>% 
               dplyr::select(TrophicSpecies, FunctionalGroup, TotalDegree, NumPrey, NumPred, Between, Close, TL, meanTrophicSimil, TopRole) %>% 
               arrange(., desc(TotalDegree)) %>% 
               mutate(across(where(is.numeric), round, 4),
                      FunctionalGroup = case_when(TrophicSpecies == "Brachiopoda_spp" ~ "Brachiopoda",
                                                  TrophicSpecies == "Campylaspis_spp" ~ "Cumacea",
                                                  TRUE ~ FunctionalGroup)), 
             format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Degree","NumPrey","NumPred","Between","Close","TL","TS","TR"), align = "llcccccccc", caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem. Ordered by degree (total number of interactions). Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4.5)
